%mainfile: ../master.tex
\chapter*{Preface}\label{ch:preface}
This report was created by, and is a result of the work of, group sw602f16 at Aalborg University during our bachelor project.\jenote{Akavet sætning} The intellectual property rights to all original material brought forth in this report, belong to the authors \jenote{not anymore}{named below}. Figures, data, and other resources gathered from third party sources will be referenced according to the IEEE standard. The software solution discussed in this report is open source, under the BSD version 2 license, and is freely available at \url{http://daisy-git.cs.aau.dk/zanderdk/hotMap}.

The readers of this report should be familiar with discrete mathematics, basic geometry and algebra. The report is targeted towards students in the field of computer science, like ourselves, with the purpose of evaluation.

\jenote{decide on one way to refer to us}{The authors of this report} would like to thank Davide Frazzetto for his supervision during the project. We would also like to thank Anders Nord and Mads Jensen from Alarm HS, and Søren Eskildsen from SmukFest for providing excellent feedback and suggestions\jenote{participation in interwievs and meetings? (Not quite sorue)}. Thanks also to Mikael Leicht Danielsen from Skanderborg municipality for providing map data of the SmukFest area. We would also like to thank Leif Bjørn from Telia Parken for providing crowd safety insights early in the project. Last but not least, we would like to thank all members of the aSTEP project for collaborating with us through this project.

\vspace{\baselineskip}\hfill Aalborg University, May \nth{26}, 2016
\vfill

%\noindent
%\begin{minipage}[b]{0.45\textwidth}
% \centering
% \rule{\textwidth}{0.5pt}\\
%  Alexander Krog\\
% {\footnotesize <akrog13@student.aau.dk>}
%\end{minipage}
%%
%\hfill
%%
%\begin{minipage}[b]{0.45\textwidth}
% \centering
% \rule{\textwidth}{0.5pt}\\
%  Jens Hegner Stærmose\\
% {\footnotesize <jstarm13@student.aau.dk>}
%\end{minipage}
%%
%\vspace{3\baselineskip}

%\noindent
%\begin{minipage}[b]{0.45\textwidth}
% \centering
% \rule{\textwidth}{0.5pt}\\
%  Kasper Kohsel Terndrup\\
% {\footnotesize <kternd13@student.aau.dk>}
%\end{minipage}
%%
%\hfill
%%
%\begin{minipage}[b]{0.45\textwidth}
% \centering
% \rule{\textwidth}{0.5pt}\\
%  Lasse Just Petersen\\
% {\footnotesize <ljpe12@student.aau.dk>}
%\end{minipage}
%\vspace{3\baselineskip}

%\noindent
%\begin{center}
%\begin{minipage}[b]{0.45\textwidth}
% \centering
% \rule{\textwidth}{0.5pt}\\
%  Simon Vandel Sillesen\\
% {\footnotesize <ssille13@student.aau.dk>}
%\end{minipage}
%\end{center}
%%
%\hfill
%%