\section{Second Meeting with Alarm HS}\label{sec:second_meeting_alarmhs_summary}

The meeting was held on March 22, 2016 over Skype following a semi-structured form. Participating in the meeting was Anders Nord, substitute chairman of Alarm HS. The meeting raised the following interesting points.

\begin{itemize}
    \item Anders has a contact in KST, the equivalent of Alarms HS at concerts held by the organisation Muskelsvindsfonden, and he can facilitate contact with the organisation.
    \begin{itemize}
        \item The aim would be to test the system in actual use, and additional feedback.
        \item If the contact is relevant, Anders will facilitate the contact.
    \end{itemize}
    \item A map legend explaining the colors on the heat map is necessary.
    \item Having separate toggleable overlays for the festival facilities, for example toilets, is good for the usability of the system.
    \item It is important that Alarm HS has a good overview of the number of people at the festival.
    \item The \emph{Find-my-location} button is a good feature for the personnel located around the festival area, especially in stressed situations.
    \item Anders mentioned the idea that users of the system can create events that show up on the map for other users to see.
    \begin{itemize}
        \item Example use case: Alarm HS gets a report that a fight is happening at a location. They create an event at the corresponding location. They find the closest guard to the event. The guard can now see on their map where the fight is happening, and can intervene.
    \end{itemize}
    \item The idea that Alarm HS can see the position of the guards on the map was mentioned as a good idea.
    \item It could be relevant to be able to log all data, so that in cases of accidents, one has evidence of what happened.
    \item A menu with searchable contact information about the festival workers could be a nice feature.
    \item There should be multiple users types, e.g. guards and Alarm HS.
    \item It is important to be able to restrict what information different users can see.
    \begin{itemize}
        \item Guards should only be able to see things relevant to themselves.
        \item Alarm HS should be able to only inform a subset of all guards.
    \end{itemize}
    \item Anders mentioned the idea that Alarm HS could send commands to the guards apps. For example, a command could be to focus on a specific point.
    \item An idea that festival guests can report situations on the map was mentioned.
    \item A tab with instructions for using the system could be useful.
    \item Overall the direction of the system is good, but there are still small tweaks that could be done, and additional features that could be useful to add.
    \item If we want to contact additional festivals, the organisation Dansk Live can be contacted.
\end{itemize}