\section{Problem Definition} \label{sec:problem_def}
% Motivation for our specific problem
Our group belongs to the application super-group, and as such our focus is on developing an application that provides \gls{lbs} through the use of the aSTEP core platform. Due to the large application area of LBS, the problem domain has to be limited.

During a Pearl Jam concert at Roskilde Festival of 2000, an accident claimed the lives of nine festival guests~\cite{roskilde}. This inspired a wave of increased safety measures across European festivals. This included the second largest danish festival called SmukFest. SmukFest came under scrutiny in 2013 when they were accused of letting too many people attend the Prince concert~\cite{smukfestPrince}. After a concert with Kim Larsen in 2015~\cite{kimlarsen}, SmukFest was once again under scrutiny because the show had been interrupted by safety personnel in order to avoid an accident. In many people's eyes, this called into question the SmukFest management's ability to ensure people's safety during the festival.

Due to these past events, the area of crowd safety was a particular interest for our group. We wanted to figure out how we could monitor the behaviour of large crowds using \gls{lbs}. While organisers of these events are usually able to control the total number of people entering the premises, large crowds can still pose many different problems. This is, amongst other reasons, due to the difficulty of predicting movements that happens in areas with large crowds~\cite{wirz2012inferring}. The problem is complicated further at some events, where it is not feasible for the security personnel to manually monitor the entire area at once.

% Problem statement
Therefore a \gls{lbs} application might be able to assist in the monitoring task, by gathering information about the positions and movement of the individuals in the crowd, through their mobile devices. This leads us to the problem statement for this project:

\vspace{0.5 cm}
\begin{center}
	\textbf{\textit{How can we develop an application that, using aSTEP services, can analyse position data gathered from events that attracts large crowds, identify relevant information about the behaviour of the crowds, and present this information to event staff in an intuitive manner?}}
\end{center}