\section{Report Structure} \label{sec:report_structure}
% Motivation --> study regulations

Since the report is to be evaluated as part of a bachelor project, it needs to conform to a study regulation. This study regulation emphasises the importance of using well defined software development methods and practises during the development of a complex software system, where many sub-projects have to be coordinated. In order to clearly reflect the development process and the coordination challenges, the report has been structured as follows:

\textbf{\Cref{ch:intro}:} The introduction chapter, where we introduce the motivation behind the problem, as well as the aSTEP project.

\textbf{\Cref{ch:sprint_1,ch:sprint2,ch:sprint3,ch:s4}:} In these chapters we describe the development and research done in each sprint individually.

\textbf{\Cref{ch:collab}:} This chapter describes the most important collaborations we have had with the other aSTEP groups during the semester.

\textbf{\Cref{ch:discussion}:} The chapter discusses which considerations have to be made before the system can be put in use.

\textbf{\Cref{ch:conclusion}:} The chapter in which we conclude on the project, including the developed system, collaborations, and the development process, and discuss relevant future work on the system.

\textbf{\Cref{ch:future_work}:} This chapter lists many topics which we would like to have done, but did not have the time to. If other students want to continue this project, this chapter should serve as an inspiration.

\textbf{\Cref{ch:appendix}:} The appendix contains summaries of all meetings held during the project.